Dissertation

### 2023-10-29 Manuscript/manuscript.qmd
adjust appendices
small fixes; remove prefer-html from docx render

---
code-repo: "Access the code, data, and analysis at <https://github.com/tegorman13/Dissertation>"
bibliography: ../Assets/Bib/Dissertation.bib
link-citations: true
# keep-md: true
toc: false
toc-depth: 3
toc-location: body
execute: 
  warning: false
  eval: true
  include: false
---

@@

```{r setup}
here::set_here(path='..')
source(here::here("Functions", "packages.R"))

@@

```{r}
source(here::here('Functions/IGAS_ProcessFunctions.R'))

@@

**Equation 1:** \[ Similarity\_{I,J} = \sum*{i = I}*\sum{j=J}
e^{-c^\cdot dp\_{i,j}} \]

@@

## Appendix

### Project 1 Appendix

@@

>>>>

---
code-repo: "Access the code, data, and analysis at <https://github.com/tegorman13/Dissertation>"
bibliography: ../Assets/Bib/Dissertation.bib
link-citations: true
# keep-md: true
toc: false
toc-depth: 3
toc-location: body
execute: 
  warning: false
  eval: true
  include: true
  #echo: false
---

@@

```{r setup}
#| echo: false
#| 
here::set_here(path='..')
source(here::here("Functions", "packages.R"))

@@

```{r}
#| echo: false
source(here::here('Functions/IGAS_ProcessFunctions.R'))

@@

**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J}
(e^{-c^\cdot d^{p}_{i,j}}) $$

@@

# Appendix

### Appendix - Project 1

@@

### Appendix - Project 2 - Experiment 1
